Supplementary Materials

### 2019-01-30 sup_mat/sup_mat.Rmd
Made changes to sup_mat
Removed uneeded plots and reorganised

---
title: "Supplementary Materials"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    fig_caption: yes
fig_height: 4
fig_width: 6
---

@@

# Participants

```{r Participants, echo = FALSE}
# sort out participants 
ls_acc_RT$observer <- as.numeric(as.factor(as.numeric(ls_acc_RT$observer)))

@@

## Participant exclusions in the Split-Half task
Accuracy data is shown in Figure \ref{fig:acc_plt}. From this we can see that there are a number of participants who did not perform the task to a reasonable standard: 15, 25, 47, and 48. These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials. After removing these participants, the lowest accuracy in either session was `r paste(min_easy,"%", sep = "")` for the easy targets, and `r paste(min_absent, "%", sep = "")` for target absent trials. This leaves us with `r length(unique(avg_acc_all$observer))` participants for the split-half paradigm.

```{r acc_plt, fig.cap = "\\label{fig:acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
# make the plot
plt <- ls_acc_RT %>%
  group_by(observer, targSide, session) %>%
  summarise(Accuracy = mean(accuracy)) %>%
  ggplot(aes(targSide, Accuracy, fill = session)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  scale_y_continuous(breaks = c(0,1)) + 
  theme_bw() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), legend.position = "top", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) + 
  scale_fill_ptol() +
  facet_wrap(~observer)
plt$labels$x <- "Target Condition"
plt
```

```{r rt_plt, fig.cap = "\\label{fig:rt_plt} Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt <- ls_acc_RT %>%
  ggplot(aes(rt)) + 
  geom_histogram() + 
  theme_bw() +  
  facet_wrap(~targSide)
plt$labels$x <- "Response Time (msecs)"
plt2 <- ls_acc_RT %>%
  mutate(log2_RT = log2(rt)) %>%
  ggplot(aes(log2_RT)) + 
  geom_histogram() + 
  theme_bw() +
  facet_wrap(~ targSide)
plt2$labels$x <- "log2 Response Time"

# put together 
grid.arrange(plt,plt2)
```

# Data Processing

The

## Split-Half 
`r invalid_kp` trials with invalid key responses were removed. After removing data from the four outlier participants (see above), all remaining incorrect trials (n = `r incorrect_trials$n[incorrect_trials$accuracy == 0]`) were removed, leaving a total of `r incorrect_trials$n[incorrect_trials$accuracy == 1]` trials over 60 participants.

### Reaction Times 
As expected, reaction times were highly skewed (Figure \ref{fig:rt_plt}), so were log2 transformed (in ms units) before the participant means were calculated for each session and target condition (Figure \ref{fig:rt_plt})

### Eye Movements
`r num_fixations` fixations were recorded. Of these, `r num_removed` fell outside of the stimulus area and were removed. Fixations landing within a vertical strip consisting of 10% of the stimuli's width were classed as central. All remaining fixations were then classed as landing on the homogeneous or heterogeneous half of the stimulus. Initial fixations were not included in the analysis. Numbers of fixations are given in Table \ref{tab:table}.

# make table 
kable(table_dat)
```

## Adaptive Choice
```{r ACS plotting, echo = FALSE, message = FALSE, fig.align = "center"}
# what sort of things do we care about....

@@

```
A participant was excluded if their accuracy in the task was more than 3 standard deviations below the average for all participants. Participants `r paste(excluded[1], "&", excluded[2])` were excluded for having an accuracy that was 3 standard deviations below the global average of `r round(avg_1, digits = 2)`.

```{r ACS_rt, fig.cap = "\\label{fig:ACS_rt_plt} Distribution of reaction times in Adaptive Choice paradigm. Optimal choice corresponds to reporting the number that was in the box with the minority colour group.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
grid.arrange(plt_ACS_rt_opt, plt_ACS_logrt_opt)
```

```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_meanrt_opt
```

```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_mean_acc
```

## Foraging

@@

>>>>

---
title: "Supplementary Materials"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
    fig_caption: yes
fig_height: 4
fig_width: 6
---

@@

# Data Processing
## Participant Exclusions
```{r Participants, echo = FALSE}
# sort out participants 
ls_acc_RT$observer <- as.numeric(as.factor(as.numeric(ls_acc_RT$observer)))

@@

### Split-Half task
Accuracy data is shown in Figure \ref{fig:ls_acc_plt}. From this we can see that there are a number of participants who did not perform the task to a reasonable standard: 15, 25, 47, and 48. These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials. After removing these participants, the lowest accuracy in either session was `r paste(min_easy,"%", sep = "")` for the easy targets, and `r paste(min_absent, "%", sep = "")` for target absent trials. This leaves us with `r length(unique(avg_acc_all$observer))` participants for the split-half paradigm.

```{r ls_acc_plt, fig.cap = "\\label{fig:ls_acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
# make the plot
plt <- ls_acc_RT %>%
  group_by(observer, targSide, session) %>%
  summarise(Accuracy = mean(accuracy)) %>%
  ggplot(aes(targSide, Accuracy, fill = session)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  scale_y_continuous(breaks = c(0,1)) + 
  theme_bw() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), legend.position = "top", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) + 
  scale_fill_ptol() +
  facet_wrap(~observer)
plt$labels$x <- "Target Condition"
plt
```

### Adaptive Choice
```{r ACS plotting, echo = FALSE, message = FALSE, fig.align = "center"}
# what sort of things do we care about....

@@

```
A participant was excluded if their accuracy in the task was more than 3 standard deviations below the average for all participants. As can be seen in Figure \ref{fig:ACS_acc}, participants `r paste(excluded[1], "&", excluded[2])` were excluded for having an accuracy that was 3 standard deviations below the global average of `r round(avg_1, digits = 2)`.

```{r ACS_rt, fig.cap = "\\label{fig:ACS_rt_plt} Distribution of reaction times in Adaptive Choice paradigm. Optimal choice corresponds to reporting the number that was in the box with the minority colour group.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
# grid.arrange(plt_ACS_rt_opt, plt_ACS_logrt_opt)
```

```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
# plt_ACS_meanrt_opt
```

```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_mean_acc
```
### Foraging
No participants were exlucded from the analysis of these data. However, participants 27, 40, 41, 42, and 43 were missing their data from the Feature search condition (Figure \ref{fig:For_switch_rt})

@@

## Data Processing
### Response Times 
Response Times in the Adaptive Choice and Split-Half tasks were normalised by applying a log2 transformation to the data as can be seen in Figure \ref{fig:ACS_SH_rt}. Also, response times that were 3 standard deviations from the mean were discarded.

```{r ACS_SH_rt, fig.cap = "\\label{fig:ACS_SH_rt} Log2 transformed Response time distributions for the Split-Half (top) and Adaptive Choice (bottom) tasks. The plot for the Adaptive Choice task is split between RTs for optimal choices (i.e. picking the colour in the minority as indicated by a 1) and the suboptimal choice", echo = F, warnings = F, message = F, fig.align = "centre"}
# make rt plots 
# do SH first 
plt_sh_rt <- ls_acc_RT %>%
  mutate(log2rt = log2(rt)) %>%
  ggplot(aes(log2rt)) + 
  geom_histogram() + 
  theme_bw() + 
  facet_wrap(~targSide)
plt_sh_rt$labels$x <- "Log2 Response Time (msecs)"

plt_acs_logrt <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice),
         sdev = sd(log2_RT),
         mean_rt = mean(log2_RT)) %>%
  filter(log2_RT > mean_rt - 3*sdev,
         log2_RT < mean_rt + 3*sdev,
         log2_RT > log2(300)) %>%  
  ggplot(aes(log2_RT,
             colour = Optimal_Choice,
             fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(legend.position = "bottom",
        strip.text.x = element_blank()) + 
  scale_colour_ptol() + 
  scale_fill_ptol() + 
  facet_wrap(~Optimal_Choice)
plt_acs_logrt$labels$x <- "Log2 Response Time (msecs)"

grid.arrange(plt_sh_rt, plt_acs_logrt, ncol = 1)

```
### Split-Half

#### Invalid responses
`r invalid_kp` trials with invalid key responses were removed. After removing data from the four outlier participants (see above), all remaining incorrect trials (n = `r incorrect_trials$n[incorrect_trials$accuracy == 0]`) were removed, leaving a total of `r incorrect_trials$n[incorrect_trials$accuracy == 1]` trials over 60 participants.

```{r, echo = F, include = F}
#Reaction Times 
#As expected, reaction times were highly skewed (Figure \ref{fig:ls_rt_plt}), so were log2 transformed (in ms units) before the participant means were calculated for each session and target condition (Figure \ref{fig:ls_rt_plt})
```
#### Eye Movements
`r num_fixations` fixations were recorded. Of these, `r num_removed` fell outside of the stimulus area and were removed. Fixations landing within a vertical strip consisting of 10% of the stimuli's width were classed as central. All remaining fixations were then classed as landing on the homogeneous or heterogeneous half of the stimulus. Initial fixations were not included in the analysis. Numbers of fixations are given in Table \ref{tab:table}.

# make table 
kable(table_dat, caption = "\\label{tab:table} No. of fixations to each side in each condition.")
```
